### 2024-12-06 paper/sections/abstract.tex
feat: completed abstract & introduction, started on related works and mostly finished on eval

\documentclass[../main.tex]{subfiles}
\begin{document}
Your abstract text goes here. Just a few facts. Whet our appetites.
Not more than 200 words, if possible, and preferably closer to 150.
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
Implementing new CCAs (congestion control algorithms) is traditionally a time-consuming and error-prone process. Developing new CCAs directly in the kernel not only requires the developer to have advanced knowledge about kernel programming, but also still introduces opportunities for potentially fatal bugs that will crash the kernel. Furthermore, the development and testing process is made slow from the constant need to reboot and difficulties in running. While developing CCAs as kernel modules (https://pbg.cs.illinois.edu/papers/jay18pcc-kernel.pdf) has traditionally been an accepted alternative, running developmental software directly in the kernel still introduces instability and crashes. Recent research, such as CCP (CCP), explored the possibility of developing and running CCAs in userspace, having the algorithm communicate with the kernel through a developer-friendly datapath api that is vetted for safety. Simultaneously, developing CCAs in eBPF (https://dl.acm.org/doi/10.1145/3609021.3609295) has been explored as a new alternative as the eBPF verifier checks the provided program for issues like memory-safety violations and infinite loops. In this paper, we will evaluate the different approaches to CCA development by measuring their behavioral correctness and performance cost. 
\end{document}

### 2024-12-06 paper/sections/evaluation.tex
paper: add template
feat: completed abstract & introduction, started on related works and mostly finished on eval

\documentclass[../main.tex]{subfiles}
\begin{document}
Design
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
We included two sets of benchmarks: a behavioral benchmark aimed to verify the "correctness" of different implementations (TCP Cubic should behave similarly no matter where it is implemented, as indicated by metrics such as bitrate/congestion window size over time), and a performance benchmark aimed to measure the CPU overhead of different implementation approaches. A CCA implementation with smaller CPU overhead would logically lead to a higher maximum bandwidth in an ideal, infinite-speed connection where the CPU running the CCA is the bottleneck. \\
Our benchmarks are ran with iperf3 (cite). For each trial, we loop through every CCA we are testing and run iperf3 for 15 seconds. At the same time, we run a Python script that loops infinitely and adds 1 to an accumulator at every loop. Once the 15 seconds are up, the script then outputs the final number into a file, a higher number suggesting that the script was able to access more CPU cycles. We run 20 trials to ensure statistical reliability. \\
After all the trials, we average the behavioral metric across the trials and plot the average for each CCA through time as the behavioral benchmark. We then plot the CPU performances for each CCA across trials on a boxplot. In order to make sure we are correctly benchmarking the performance impact of CCAs instead of confounding factors, we ran the benchmark on an out-of-the-box Debian images on a VM. To ensure the CPU benchmark and the CCA are running on the same CPU, our VM is set up to contain only one core. [Results and interpretations]
\end{document}

### 2024-12-06 paper/sections/introduction.tex
feat: completed abstract & introduction, started on related works and mostly finished on eval

\documentclass[../main.tex]{subfiles}
\begin{document}
A paragraph of text goes here. Lots of text. Plenty of interesting
text. Text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text.
More fascinating text. Features galore, plethora of promises.
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
Congestion Control Algorithms form a critical part of the Internet ecosystem. While traditional discussions about CCAs centered around ideas like fairness between users (cite flow-based fairness/tcp friendly paper here), newer research explored potentials for CCAs to improve network performance (cite BBR?) and allow the user to customize bandwidth allocated to different applications on the same machine. Research on various old and new congestion control algorithms is critical to the stable operation and continuous improvement of the Internet. \\
The development of new CCAs faced two problems. The first problem being the high friction of development: CCAs have traditionally ran inside the networking stack in the kernel. As a result, developer of new CCAs are required to program in a kernel environment, forming a high barrier of entry and enabling potential high-impact bugs. The second problem being the difficulties of distribution. Though some have argued for abolishing the idea of flow-based fairness (Dismantling), TCP-Friendliness has nevertheless remained a central piece for any CCA-related research. To correctly evaluated the impacts of a new CCA on the Internet ecosystem, we need to be able to see significant real-world adoption from actual users around the world. Pushing a new, untested CCA upstream to the Linux kernel is an extremely difficult, if not outright impossible task. As a result, any CCA wishing to see eventual large-scale adoption must first propose a relatively user-friendly way for people to adopt it in the early stages. \\
We believe that eBPF as a platform for implementing congestion control solves both problems. On the friction side, while programming in eBPF still requires a non-negligible amount of domain expertise, the process is nevertheless much simpler when compared to developing kernel modules, for example. The runtime-attached nature of eBPF makes iterating and testing new versions much easier. Furthermore, the eBPF VM and Verifier provide powerful guarantees to the safety of the program, protecting against large amounts of hard-to-solve bugs that lead to the kernel crashing. On the adoption side, the safety guarantees provided by eBPF will greatly encourage user adoption. While users can be hesitant in installing kernel patches or modules, attaching a eBPF program is much lower-risk and appealing if the new CCA itself promises significant improvements.\\
Despite these upsides, running CCAs in eBPF can possibly incur extra costs due to running in the eBPF VM. By instrumenting the performance overheads of various different ways of implementing CCAs, we would like to explore whether eBPF is a viable long-term platform to implement CCAs on, or would researchers be better-off to switch to a kernel space implementation once a proof-of-concept was done on eBPF. In addition to CCAs directly implemented in eBPF, we also tested other means of developing CCAs quickly and safely. The Congestion Control Plane (CCP) (cite CCP) is an idea proposed to implement CCAs in user space. Since the original CCP kernel datapath is written as a Linux kernel module, we also implemented an alternative datapath in eBPF to potentially take advantage of the safety guarantees.
\end{document}

### 2024-12-06 paper/sections/relatedwork.tex
paper: add template
feat: completed abstract & introduction, started on related works and mostly finished on eval

\documentclass[../main.tex]{subfiles}
\begin{document}
A paragraph of text goes here. Lots of text. Plenty of interesting
text. Text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text.
More fascinating text. Features galore, plethora of promises.
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
CCP decoupled data gathering and CCA computation. A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state. Platform/OS independence
\end{document}
